\documentclass[10pt,a4paper]{article}
\usepackage[margin=1cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0em}
\setlength{\parskip}{0pt plus 1pt minus 1pt}
\renewcommand{\baselinestretch}{1}

\setlist[itemize]{topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0pt, leftmargin=1cm}


\begin{document}

\titlespacing*{\section}{0pt}{0pt}{10pt} 
\titlespacing*{\subsection}{0pt}{10pt}{5pt} 

\pagestyle{empty}

{
\centering
{\Huge\textbf{Daniel Andres Jimenez Riveros, MSc-MA}}\\
\medskip 
Vancouver, BC, Canada \textbar\ \href{mailto:da.jimenez166@gmail.com}{da.jimenez166@gmail.com} \textbar\ \href{https://www.linkedin.com/in/daniel-jimenez-78500117a/}{linkedin.com/in/daniel-jimenez-78500117a}\\
}

\rule{\textwidth}{0.4pt} 

\section*{Professional Summary}
Software Developer Engineer with a proven track record at Amazon. Designed and developed interactive front-end dashboards leveraging ReactJS, D3js, and Redux RTK, enhancing user engagement and retention. Architect and maintain scalable back-end services using Node.js, ensuring seamless data flow. Deep understanding of AWS services, deploying applications for optimal performance and scalability. Strong background in business intelligence and machine learning, driving data accessibility and business improvements.

\rule{\textwidth}{0.4pt} 

\section*{Work Experience}

\subsection*{AMAZON, Bogot치, Colombia}
\textbf{Software Developer Engineer} \hfill July 2022 - August 2023
\begin{itemize}[noitemsep]
    \item Developed advanced interactive dashboards, enhancing data analysis efficiency for 2,000+ data analysts, significantly improving decision-making speed and accuracy.
    \item Engineered responsive UI/UX front-ends with Javascript, ReactJS, D3.js, and Redux RTK, elevating user experience and interaction for key enterprise applications.
    \item Architected and deployed scalable back-end services using Typescript, ExpressJS, and NodeJS, ensuring robust performance and reliability across enterprise systems.
    \item Optimized application deployment and scalability using AWS services (EC2, S3, Lambda, DynamoDB, API Gateway).
    \item Implemented critical RESTful APIs, integrating seamlessly with three internal services, empowering over 300 team leaders in the CSBI department with enhanced data accessibility.
    \item Streamlined cloud-native application deployment processes with Amazon CDK and CloudFormation, significantly reducing deployment and maintenance time and increasing system resilience.
\end{itemize}

\textbf{Business Intelligence Analyst} \hfill July 2021 - July 2022
\begin{itemize}[noitemsep]
    \item Engineered and upheld comprehensive ETL (Extract, Transform, Load) processes, guaranteeing data integrity, completeness, and prompt availability for BI reporting.
    \item Utilized R's ggplot2 for creating dynamic, publication-quality graphs that visually represented complex analysis findings for non-technical stakeholders.
    \item Streamlined data preprocessing workflows with Python, achieving a 50\% reduction in processing time, significantly accelerating project timelines.
    \item Automated monthly performance reporting with SQL procedures, slashing manual effort by 80\% and enhancing report accuracy and timeliness
\end{itemize}

\textbf{Information Technology Intern} \hfill January 2021 - July 2021
\begin{itemize}[noitemsep]
    \item Played a key role in the front-end development of critical internal tools using JavaScript, HTML, and CSS, directly benefiting over 9,000 Amazon employees through enhanced usability and productivity.
    \item Spearheaded the design of intuitive UI components and icons with Figma, significantly improving user experience across four major internal applications.
    \item Acquired and applied knowledge of core AWS services and proprietary tools essential for application development, facilitating the robust and scalable deployment of internal applications
\end{itemize}

\subsection*{UNIVERSITY OF THE BOSQUE, Bogot치, Colombia}
\textbf{Professor, Humanities Department} \hfill August 2022 - June 2023
\begin{itemize}[noitemsep]
    \item Instructed 35 students per term in programming languages and frameworks focus in creative coding, such as ThreeJS, Arduino, C++ and D3js.
    \item Mentored students in project-based learning, offering personalized guidance and feedback to help them develop innovative digital artworks and interactive projects.
    \item Demonstrated real-world applications of coding in the arts, showcasing how todays technologies can be used to create captivating visualizations and immersive experiences.
\end{itemize}

\subsection*{AQSTICA S.A.S, Bogot치, Colombia}
\textbf{Data Analyst} \hfill February 2018 - November 2020
\begin{itemize}[noitemsep]
    \item Analyzed complex datasets to drive strategic decisions, boosting operational efficiency by 10\% in revenue
    \item Employed statistical techniques to enhance marketing targeting by 20\%, using a linear regression Model.
    \item Automated data cleaning and transformation with Python, SQL and MongoDB, enhancing data quality by 25\% and cutting processing time by 40\%.
\end{itemize}
\rule{\textwidth}{0.4pt} 
\section*{Education}

\textbf{University of British Columbia}, Vancouver, Canada \\
Master of Data Science in Computational Linguistics \hfill Coursing

\textbf{Universidad de los Andes}, Bogot치, Colombia \\
Master in Information Technology \hfill Graduation Candidate \\
Bachelor in Industrial Engineering \\
Bachelor in Arts

\rule{\textwidth}{0.4pt} 

\section*{Awards \& Achievements}

\begin{itemize}[noitemsep]
    \item COLFUTURO Scholarship \hfill 2023
    \item Data Science for All (DS4A)  \hfill 2018
\end{itemize}

\rule{\textwidth}{0.4pt} 
\section*{Skills}

Python, Typescript, Javascript, ReactJS, Nodejs, Flask, C++, Java, HTML, CSS, R, SQL, MongoDB, Figma, Adobe XD, Premier Pro, Photoshop, Illustrator, Microsoft Suite.

\end{document}
